### 2024-08-11 doc/Thesis/chapter/052-post-emma.tex
start doing todo.md

%\textbf{Pre-writing:}
%\Gls{anova} doesn't provide a lot of extra information. 
%wrong the second is not for phd but for extended data set
%but for phd even lower than 0.1 \%
%Anova shows that the influence of TCal is significant as shown by the F

@@

%\todo{what was fitted how?}
The data obtained from the \gls{emma} optimization was used to fit a linear model. 
The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
The coefficients of the $n_L$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too. 
%
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot n_L -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot n_L \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot n_L - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
%			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign 
except $c_{zr}$ and the intercept. 
%
More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e. a negative influence on the resistance 
and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the whole data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
$v_{cal}$ and $n_L$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $n_L$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\hat\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\hat\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\, $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{C}$. 
The biggest influence on $\hat\rho$ is  $n_L$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $n_L$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artifact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

>>>>

%\textbf{Pre-writing:}
%\Gls{anova} does not provide a lot of extra information. 
%wrong the second is not for phd but for extended data set
%but for phd even lower than 0.1 \%
%Anova shows that the influence of TCal is significant as shown by the F

@@

%\todo{what was fitted how?}
The data obtained from the \gls{emma} optimization was used to fit a linear model. 
The biggest difference between the linear model and \gls{emma} is that the linear regression function will include all input variables, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
The coefficients of the $n_L$ term have the same sign in equations \ref{eq:emma-phd3}, \ref{eq:emma-G3}, \ref{eq:emma-phd4}, \ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd}, \ref{eq:linreg-G} and have comparable magnitudes too. 
%
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot n_L -0.0029\cdot v_{C} + 0.0058\cdot T_{C} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} =&  \,\,\qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot n_L \,\,\quad - 1.2\cdot v_{C}  \,\,\,\quad +0.2\cdot T_{C} \\
			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot n_L - 1.2\cdot v_{C} + 0.2\cdot T_{C} \\
%			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign 
except $c_{zr}$ and the intercept. 
%
More particularly, $T_{cal}$ and $T_{C}$ have positive coefficients, i.e.\ a negative influence on the resistance 
and $n_L$, $v_{C}$ and $v_{cal}$ have negative coefficients, i.e.\ a positive influence on resistance. 
An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the whole data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
$v_{cal}$ and $n_L$ are perfectly predicted by linear regression as there is an exact direct proportionality and thus are not displayed here. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $n_L$     & $v_{C}$      & $T_{C}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\hat\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\hat\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $n_L$ are largest in value, but the values which are factored with these coefficients - i.e.\ $c_{zr}$ and $n_L$ themselves -- are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
For better comparison, the influence of an input variable was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{i,min}+x_{i,max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{C}$. 
The biggest influence on $\hat\rho$ is  $n_L$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well, it is noteworthy that $n_L$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artifact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $n_L$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

### 2024-08-11 doc/Thesis/chapter/053-discussion.tex
start doing todo.md

The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself.\cite{cherkassky1998learning} %(page 25)

@@

which is low in comparison with literature consulted
\cite{

@@

%	\item How to measure model complexity (i.e. flexibility to fit the training data)?

@@

    \item \textbf{objective} should be defined as clear as possible. It will help to set a clear goal for each todo, e.g. the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using} Which question should be answered and aufstellen a null Hypothesis. This is often very trivial, but let's you focus on the correct path. 

@@

\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables. \cite{cherkassky1998learning}

@@

    \item \textbf{pre-optimization}{The primary goal of a screening experiment is to identify the active factors. A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $2\cdot6=12$ experiments. Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
    \item \textbf{factorial design} (classical \gls{doe}) is more robust at feature extraction for error laden data \cite{giunta2003overview} putting data on the extrems makes trend extraction easier. "By moving the samples to the boundaries of the design space, the effect of the random error terms is reduced."

@@

%-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2009}
%but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?

@@

goal is to estimate function with finite samples, so it's always inaccurate (biased). 

>>>>

The selection of input and output variables, data encoding/representation and incorporating a prior knowledge into the design of the learning system is often more critical for an overall success than the design of the learning machine itself\cite{cherkassky1998learning}. %(page 25)

@@

which is low in comparison with literature consulted\cite{

@@

%	\item How to measure model complexity (i.e.\ flexibility to fit the training data)?

@@

    \item \textbf{objective} should be defined as clear as possible. It will help to set a clear goal for each todo, e.g.\ the primary goal of a screening experiment is to identify the active factors\cite{miller2001using}. Which question should be answered and aufstellen a null Hypothesis. This is often very trivial, but let's you focus on the correct path. 

@@

\textbf{6. Interpret the Model and Drawing Conclusions} The interpretability and accuracy of the model are compete. In classical statistics such as linearly parametrized function will suit both requirements. More complex and flexible models might lead to better estimates with less interpretability. Identifying the most important input variables\cite{cherkassky1998learning}.

@@

    \item \textbf{pre-optimization}{The primary goal of a screening experiment is to identify the active factors. A secondary goal is to provide a simple model that captures the essential features of the relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}} But $2^6=64$ are too many for preliminary test so maybe check base and from there do $2\cdot6=12$ experiments. Then focus on selected input vars, which might have mutliple maxima \\ \td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see Miller 2001\cite{miller2001using} section 1) }
    \item \textbf{factorial design} (classical \gls{doe}) is more robust at feature extraction for error laden data\cite{giunta2003overview} putting data on the extrems makes trend extraction easier. "By moving the samples to the boundaries of the design space, the effect of the random error terms is reduced."

@@

%-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e.,\ that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2009}
%but on the other hand: If one is not sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?

@@

goal is to estimate function with finite samples, so it is always inaccurate (biased). 
